\subsection*{Product Risks}
Insufficient Selection of Card Designs: Having a choice of card designs to choose from is most strongly associated with the functional values which drive consumer choice. An insufficient choice of designs for the consumer will mean their functional needs may not be fulfilled beyond what our competitors can offer. Furthermore, a poor selection of designs can lead to the non fulfilment of social values in the case where the cards do not portray the social image of the consumer. Lastly, if the offered designs cause a negative emotional response in the recipient, it is unlikely that the emotional and belonging needs of the consumer will be fulfilled. The fulfilment of all needs is key to getting customers to join our service.

\subsection*{Industry Risks}
As in any industry with competition, there are a number of risks involved. One of the largest risks of any startup is lack of demand. Given that the card market is already well-served, we are counting on our unique selling point to win customers. However, this carries the risk that these customers will not value our selling points highly enough to warrant changing their habits to involve a subscription service. To mitigate this, it may be necessary to advertise directly to our target audience.

Another risk is that, given the low entry barrier to starting our business, it would be trivial for a company with more advertising resources (such as Hallmark) to duplicate our service. This is compounded by the fact that our idea is too simple to protect through legal devices like patents. To mitigate this, we aim to target a section of the market which is currently underserved by the majority of the established companies---even if Hallmark were to duplicate our service, they'd still be selling Hallmark cards rather than handmade ones, thus appealing to different audiences.

In order to supply through Etsy's or Redbubble's wholesale scheme, we need to submit an application giving details about our business. There is a risk that this application could be rejected, in which case we would need to consider other supply options. We should take great care to make our application as strong as possible to try and avoid this situation, perhaps by having a completed website before making the application so we have something tangible to show them. There is also the risk that these companies change their terms of service once we are somewhat reliant on them, e.g.\ taking a bigger cut from the sellers and allowing them to sell at a higher wholesale rate in return.

\subsection*{Market Validation Risks}
Research conducted during market validation found that while the greetings card industry is growing in the UK, it is declining globally due to competition with online social websites. A potential risk to our service is an unexpected eventual decline in the UK market making it more difficult for us to compete. This can be mitigated by setting ourselves apart from the competition by targeting a higher end audience and marketing the service to focus on the meaning behind sending the card.