Our team consists of 6 team members. We are each technically proficient, but also bring unique sets of skills to the mix.

The team member predominantly skilled in front-end development and user interfaces is Darien. He has had experience with building user interfaces, and is our team’s creative flair. He has already produced prototype user interfaces for a trial web application that we will use to determine whether there is a market for our business idea. His skills will be required to build a fully functioning, responsive UI for the business idea.

Caroline has experience across the stack, and specialises in A/B testing and big data. She will be able to run A/B tests on the website and use experimental design in order to make design decisions that will maximise conversion. She has experience with the workings of a real business, and understands the importance of communication and the soft skills required to run a successful company.

Ben and Max are both predominantly skilled in back-end development; skills which will be necessary if our trial website is a success and we are to develop a fully functioning system. They are both very strong coders, with a considerable amount of experience working in tech.

Ben already has produced system designs for the back-end of the website using python and PostgreSQL, both of which he is proficient in. He also has investigated the financial aspects of our business, therefore he will be the one to manage our business’ finances. Max is knowledgeable in the legal requirements surrounding our business, and will ensure that we act in compliance with any relevant laws.

Ollie is a hard-working team member, skilled across the stack. He also has experience in developing mobile applications, meaning that we will have the ability to also produce a mobile app for our business idea. He is very organised and determined, and will take the time to help other team members with their work if they are struggling. He helps to keep the team morale high.

Will is skilled with using front-end frameworks such as React and AngularJS. This is useful as we would most likely need to implement our website with one of these frameworks. Furthermore, his efficient team organisation and management makes him an essential part of the team. He regularly ensures that everyone knows what they are doing and keeps the group communicating regularly. He is a good speaker and can pitch a business idea well, making him essential for the marketing of our business.

We believe that our team will enable our business to succeed, due to our mix of solid  technical skills and equally necessary soft skills.
